---
title: "The 'gfilinreg' package"
output: 
  rmarkdown::html_vignette:
    css: vignette.css
vignette: >
  %\VignetteIndexEntry{The 'gfilinreg' package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  fig.width = 5, fig.height = 4.5
)
```

The main function of the 'gfilinreg' package, namely `gfilinreg`, returns some 
weighted samples of the generalized fiducial distribution of the parameters of 
a linear regression model whose error terms are distributed according to a 
Gaussian, Student, Cauchy, or a logistic distribution.

Let's have a look at a simple linear regression model with Gaussian errors:

```{r simplereg}
library(gfilinreg)
set.seed(666L)
x <- rgamma(6L, shape = 10, rate = 1)
y <- rnorm(6L, mean = x, sd = 2)
dat <- data.frame(x = x, y = y)
fidsamples <- gfilinreg(y ~ x, data = dat, distr = "normal", L = 150L)
```

The algorithm involves a partition of the hypercube ${(0,1)}^{p+1}$, where $p$ 
is the dimension of the model (the number of columns of the $X$ matrix), and 
the integer argument `L` of the `gfilinreg` function is the desired number of 
subdivisions of each edge of the hypercube.

A quick summary of the fiducial samples is provided by the `gfiSummary` 
function: 

```{r simplereg_summary}
gfiSummary(fidsamples)
```

Let's compare with `lm`:

```{r simplereg_lm}
lmfit <- lm(y ~ x, data = dat)
coefficients(lmfit)
sigma(lmfit)
confint(lmfit)
```

Excepted for the scale parameter $\sigma$, results are very similar.

One can generate simulations of fiducial predictive distributions and, based on 
these distributions, one can get fiducial prediction intervals:

```{r simplereg_predictions}
new <- data.frame(x = c(9, 10, 11))
fidpred <- gfilinregPredictive(fidsamples, newdata = new)
gfiSummary(fidpred)
predict(lmfit, newdata = new, interval = "prediction")
```

Again, there is a strong agreement between the fiducial results and the 
frequentist results.


## A small simulation study with Cauchy errors

Now we perform some simulations of a "t-test model" with Cauchy errors, we 
store the fiducial summaries for each simulated dataset and we also store the 
maximum likelihood estimates thanks to the 'heavy' package. We simulate $500$ 
datasets.

```{r simulations, eval=FALSE}
library(gfilinreg)
library(heavy)
library(data.table)

nsims <- 500L
MAXLHD <- matrix(NA_real_, nrow = nsims, ncol = 3L)
colnames(MAXLHD) <- c("group1", "group2", "sigma")
FIDlist <- vector("list", length = nsims)

group <- gl(2L, 6L)
set.seed(666L)

for(i in 1L:nsims){
  # simulated dataset
  dat <- data.frame(
    group = group,
    y = c(rcauchy(6L), 2 + rcauchy(6L))
  )
  # max-likelihood estimates
  hfit <- heavyLm(y ~ 0 + group, data = dat, family = Cauchy())
  MAXLHD[i, ] <- c(hfit[["coefficients"]], sqrt(hfit[["sigma2"]]))
  # fiducial stuff
  fidsamples <- gfilinreg(y ~ 0 + group, data = dat, L = 100L, distr = "cauchy")
  FIDlist[[i]] <- cbind(
    parameter = c("group1", "group2", "sigma"), 
    as.data.table(gfiSummary(fidsamples))
  )
}
FID <- rbindlist(FIDlist)
```

